---
title: "Assignment 2 - The tidyverse"
author: "Hyebin-Hong"
date: "`r format(Sys.time(), '%B %d, %Y | %H:%M:%S | %Z')`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    number_sections: no
    theme: cosmo
    toc: no
---
  
<style>
div.answer {background-color:#f3f0ff; border-radius: 5px; padding: 20px;}
</style>

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      error = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      comment = NA)
```

<!-- Do not forget to input your Github username in the YAML configuration up there --> 

***

```{r, include = T}
library(devtools)
library(tidyverse)
library(dplyr)
library(tibble)
library(legislatoR)
```

<br>

### Getting started with the Comparative Legislators Database

The Comparative Legislators Database (CLD) includes political, sociodemographic, career, online presence, public attention, and visual information for over 45,000 contemporary and historical politicians from ten countries (see the [corresponding article](https://www.cambridge.org/core/journals/british-journal-of-political-science/article/comparative-legislators-database/D28BB58A8B2C08C8593DB741F42C18B2) for more information). It can be accessed via `legislatoR` - an R package that is available on both [CRAN](https://cran.r-project.org/web/packages/legislatoR/index.html) and [GitHub](https://github.com/saschagobel/legislatoR).

Before you start with the following tasks, skim the tutorial to make yourself familiar with the database. You find it [here](https://cran.r-project.org/web/packages/legislatoR/vignettes/legislatoR.html).

For the following tasks, you will work with ONE of the legislatures. The legislature you'll work with depends on your prename:

| Your prename starts with... | Legislature | Code |
|---------|-------|-------|
| A-C | Austrian Nationalrat | `aut` |
| D-F | Canadian House of Commons | `can` |
| G-I | Czech Poslanecka Snemovna | `cze` |
| J-L | Spanish Congreso de los Diputados | `esp` |
| M-O | French Assemblée | `fra` |
| P-R | German Bundestag | `deu` |
| S-U | Irish Dail | `irl` |
| V-X | UK House of Commons | `gbr` |
| Y-Z | US House of Representatives  | `usa_house` |

The following tasks will be based on data from the `core` and `political` tables of the database.

<br>

***

### Task 1 - Fun with descriptives [8 points in total]

a) What's the overall share of female legislators in the entire dataset? [1 point]

```{r}


cze_whole <- get_core(legislature = "cze")

cze_female <- filter(get_core(legislature = "cze"), sex == "female")

nrow(cze_female)/nrow(cze_whole)


```

b) How many (both in absolute and relative terms) legislators died in the same place they were born in? [1 point]

```{r}

length(which(cze_whole$birthplace == cze_whole$deathplace))

```

c) Create a new variable `age_at_death` that reports the age at which legislators died. Then, plot the distribution of that variable for the entire dataset. [2 points]

```{r}

age_at_death <- as.vector(na.omit(strtoi(substr(cze_whole$death,1,4)) - strtoi(substr(cze_whole$birth,1,4))))

hist(age_at_death)

```

d) Provide one single table that provides the 5 legislators with the highest and lowest age at death, ignoring ties. [2 points]

```{r}
legis <- as.vector(strtoi(substr(cze_whole$death,1,4)) - strtoi(substr(cze_whole$birth,1,4)))

mydata <- data.frame(legis, cze_whole$name)

high <- mydata %>%
  arrange(desc(legis)) %>%
  slice(1:5)

low <- mydata %>%
  arrange(legis) %>%
  slice(1:5)

table <- data.frame(high,low)
table
```

e) Find out who has got the longest name and who the shortest (both in terms of number of characters, ignoring whitespace)! [2 points]

```{r}
counting_name <-nchar(cze_whole$name)
name <- data.frame(cze_whole$name,counting_name)

name_sort <- arrange(name,desc(counting_name))

name_sort$cze_whole.name[1]
name_sort$cze_whole.name[nrow(name_sort)]


```

<br>
<div class = "answer">
longest name:Zuzana Majerová Zahradníková
shortest name:Dan Ťok
</div>

***

### Task 2 - Exploring trends in the data [8 points in total]

a) Using data from all sessions, provide a plot that shows the share of female legislators by session! [3 points]

```{r}
leg = c("aut", "can", "cze", "fra", "deu","irl","sco","esp","gbr","usa_house/usa_senate")
ratio=list()
for (i in (1:9)) {
  cont = leg[i]
  whole <- get_core(legislature = cont)
  female <- filter(get_core(legislature = cont), sex == "female")
  ratio[length(ratio) +1]= nrow(female)/nrow(whole)
}

barplot(unlist(ratio), name.arg = c("aut", "can", "cze", "fra", "deu","irl","sco","esp","gbr","usa_house/usa_senate"), xlab = "by session", ylab = "share of female")


```

b) Explore another relation of variables in the dataset. Your analysis should (i) use data from both the `core` and the `political` table and (ii) feature data from several sessions. Also, offer a brief description and interpretation of your findings! [5 points]

```{r}
deu_subset <- inner_join(x = get_core(legislature = "deu"),
                         y = filter(get_political(legislature = "deu"), 
                                    party %in% c("CDU", "CSU", "AfD")),
                         by = "pageid")
summary(deu_subset)

```

<div class = "answer">
I have made a summary table for German legislatures from CDU, CSU and AFD. 
</div>

<br>

***

### Task 3 - Fun with functions [3 points in total]

a) Program a function `ultimate_answer()` that always returns the number 42, and prove that it works! [1 point]

```{r}
ultimate_answer <- function(...) 42L 
ultimate_answer(10, c = 56,30)

```

b) Program a robust function `normalize()` that normalizes a numeric vector x to mean(x) = 0 and sd(x) = 1! Then, apply it to all numeric variables in the mtcars dataset! [2 points]

```{r}
normalize <- function(x) {
  (x*min(x)) = 0 &
  sd(x) = 1
}


```



